\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\geometry{margin=1in}

\begin{document}

\begin{center}
    {\Huge \textbf{NGUYEN THAI SON}} \\
    \vspace{6pt}
    \textbf{DevOps Engineer} \\
    \vspace{6pt}
    \begin{tabular}{ll}
        \textbf{Phone:} & +84 396 161 954 \\
        \textbf{Email:} & sonnhat129@gmail.com \\
        \textbf{LinkedIn:} & \href{https://www.linkedin.com/in/son-n-114539152/}{linkedin.com/in/son-n-114539152/} \\
        \textbf{Github:} & \href{https://github.com/sonnguyenHT}{github.com/sonnguyenHT} \\
        \textbf{Website:} & \href{https://thaisonhtportfolio.vercel.app/}{thaisonhtportfolio.vercel.app} \\
        \textbf{Location:} & Ho Chi Minh City, Vietnam \\
    \end{tabular}
\end{center}

\vspace{10pt}
\section*{Summary}
I have practical experience in deploying and overseeing cloud-based, on-premise applications and services. Skilled in Python and Bash scripting, I have a strong grasp of networking and security concepts. My expertise includes cloud computing technologies, focusing on AWS, Azure, and Kubernetes (K8S) for container orchestration.

\vspace{5pt}
\section*{Skills}
\begin{itemize}[leftmargin=0.5in]
    \item \textbf{Programming:} Python, Bash
    \item \textbf{Operating Systems:} Linux, Windows
    \item \textbf{Relational Databases:} MySQL, PostgreSQL
    % , Oracle(pending)
    % \item \textbf{NoSQL Databases:} MongoDB(pending), Couchbase
    % \item \textbf{Cache:} Redis(pending), Memcached(pending)
    \item \textbf{Infrastructure as Code:} Terraform, Terragrunt, Ansible
    \item \textbf{Cloud Services:} AWS, Azure
    \item \textbf{Version Control:} Git
    % \item \textbf{Virtualization:} VMware, VirtualBox, QEMU(pending),
    % \item \textbf{Setup virtualmachines: } Lima(pending)(use base QEMU), Vagrant(virtualbox tick)(QEMU haven't)
    \item \textbf{Containerization:} Docker
    % , Podman(pending)
    \item \textbf{Container Orchestration:} Kubernetes (K8S, K3S)
    \item \textbf{CI/CD Tools:} GitHub Actions, GitLab Actions, ArgoCD
    \item \textbf{Monitoring Tools:} Prometheus, Grafana, Loki,Logstash, Elasticsearch, Kibana
    \item \textbf{Service Mesh:} Istio
    \item \textbf{Message Queue:} Kafka
    \item \textbf{VPN:} OpenVPN, WireGuard, tailscale
    \item \textbf{AI tools:} n8n, OpenAI, MCP(model context protocol)
    % \item \textbf{Security: } Falco(K8S)(pending), Pixie(K8S)(pending)
    % \item \textbf{Others:} ArgoCD, Jenkins(pending), JMX(java exporter), ELK Stack(pending), OpenVPN, WireGuard
\end{itemize}

\vspace{10pt}
\section*{Experience}
\noindent \textbf{\href{https://www.linkedin.com/company/h3tech/posts/?feedView=all}{H3Tech, Inc.}} \hfill \textit{Ho Chi Minh City, 06/2025 - present}  \\
DevOps Engineer \\
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item \textbf{Infrastructure as Code (IaC):} Architected and deployed scalable cloud infrastructure on \textbf{GCP} using \textbf{Terraform}, including Cloud Run, Cloud SQL, Load Balancer, Cloud Armor, and Artifact Registry.
    \item \textbf{Secure Access Management:} Implemented a secure \textbf{Bastion Host} solution to manage private connections to Cloud SQL via \textbf{Identity-Aware Proxy (IAP)}, ensuring zero-exposure of database ports to the public internet.
    \item \textbf{DevSecOps Integration:} Integrated automated security scanning tools (\textbf{Trivy, Semgrep, Gitleaks}) into the CI/CD pipeline (\textbf{Cloud Build}) to detect vulnerabilities and secret leaks early in the development lifecycle.
    \item \textbf{Automated Monitoring \& Alerting:} Engineered a robust notification system using \textbf{Google Chat} integration to provide real-time updates on build/deployment status and system health.
    \item \textbf{SRE \& Observability:} Configured advanced monitoring for \textbf{SLO violations}, error rate spikes (HTTP 5xx $>$ 5\%), and critical application logs via \textbf{Cloud Logging}, enabling rapid incident response.
\end{itemize}

\vspace{10pt}
\noindent \textbf{\href{https://www.linkedin.com/company/ltvofficial/posts/?feedView=all}{LTV SOFTWARE COMPANY LIMITED}} \hfill \textit{Ho Chi Minh City, 06/2024 - 05/2025}  \\
\textit{DevOps Engineer} \\
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item \textbf{Secure Networking:} Implemented \textbf{Tailscale VPN} solutions for vessel-to-shore connectivity, ensuring encrypted and reliable communication for maritime operations.
    \item \textbf{Service Mesh \& Traffic Management:} Architected \textbf{Istio Service Mesh} on \textbf{AWS EKS} to streamline ingress traffic, mutual TLS (mTLS), and advanced routing policies.
    \item \textbf{CI/CD Optimization:} Engineered standardized pipelines for multi-platform repositories using \textbf{GitHub Actions} and \textbf{GitLab CI}, reducing deployment lead time.
    \item \textbf{Edge Computing (K3s):} Orchestrated remote service deployments and updates across vessel-based \textbf{K3s clusters}, ensuring high availability in low-bandwidth environments.
    \item \textbf{Observability:} Developed a comprehensive monitoring stack using \textbf{JMX Exporter, Prometheus}, and \textbf{Grafana} to visualize Java service metrics for both edge and cloud environments.
    \item \textbf{Centralized Logging:} Established a unified logging architecture using \textbf{Grafana Loki}, aggregating logs from all shore-based services for rapid troubleshooting.
\end{itemize}

\vspace{10pt}
\noindent \textbf{\href{https://www.linkedin.com/company/galaxy-finx/posts/?feedView=all}{GALAXY FINX JOINT STOCK COMPANY}} \hfill \textit{Ho Chi Minh City, 10/2022 - 11/2023} \\
\textit{Cloud Engineer} \\
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item \textbf{Multi-Cloud IaC:} Developed reusable \textbf{Terraform} modules for \textbf{AWS} (VPC, ALB, ASG) and \textbf{Azure} (vNet, AKS), ensuring infrastructure consistency across providers.
    \item \textbf{Infrastructure Orchestration:} Managed complex cloud states using \textbf{Terragrunt}, utilizing \textbf{AWS S3} for backend storage and \textbf{DynamoDB} for state locking.
    \item \textbf{Configuration Management:} Authored \textbf{Ansible} playbooks for automated \textbf{Couchbase} cluster provisioning, user management, and \textbf{OpenVPN} setup.
    \item \textbf{GitOps Deployment:} Implemented continuous deployment (CD) workflows using \textbf{ArgoCD} to synchronize Kubernetes manifests with Git repositories.
    \item \textbf{Containerization:} Leveraged \textbf{GitHub Actions} to automate Docker image builds and security tagging for seamless integration into the container registry.
    \item \textbf{Monitoring:} Deployed and tuned \textbf{Prometheus} and \textbf{Grafana} dashboards to monitor system health and application performance metrics.
\end{itemize}

\vspace{10pt}
% \noindent \textbf{Home Project} \hfill \textit{Ho Chi Minh City, 08/2021 - 09/2022} \\

% \vspace{5pt}
\section*{Education}
\noindent \textbf{FPT University, Ho Chi Minh City} \hfill \textit{09/2020 - 05/2024} \\
\textit{Major: Information Assurance} \\
\textit{Final GPA: 8.1/10} \\
Achievements: Good Student Award in Spring, Summer, and Fall semesters.

\vspace{5pt}
\section*{Passions}
I am eager to join a company that invests in employee growth with structured career paths and continuous learning opportunities such as training, workshops, and certifications. I am particularly passionate about optimizing CI/CD pipelines to eliminate bottlenecks and improve efficiency.

\end{document}
